Multi-domain, multilingual translation with latent multi-task group dropout

### 2022-01-14 2022/acl/acl_latex.tex
revise related work

\textbf{Language similarity} The methods developed by \citep{sen19multilingual,kong21multilingual} use language proximity to design parameter sharing strategies. The authors propose a multi-decoder model sharing the same encoder among languages and routing languages in different families to different decoders. These approaches share the same interest in expressing the proximity between tasks in the selection of task-specific parameters as our approach. However, our method learn the selection from a latent commonality in data instead of using a predefined selection such as "One language family per decoder" in \cite{kong21multilingual}.

\textbf{Language-specific sub-networks}. \todo{}\citet{Frankle19Lottery,liu18rethinking} proposed different techniques to identify most important parameters for the current task so that when training the model while masking other parameters the performance of the model does not degrade. \citet{lin21learning} hypothesized that among parameters of a multilingual NMT model, there exists a subset of parameters more biased to a specific language. The authors proposed to locate these subsets by pruning the parameters of each fine-tuned model. Our approach also aims to assign a sub-network to each task by masking the output of each layer rather than masking the parameters. Furthermore, \citet{lin21learning} computes the masks via a heuristic selection while our approach learn the masks via a variational technique.

>>>>

\textbf{Language similarity} The methods developed by \citep{sen19multilingual,kong21multilingual} use language proximity to design parameter sharing strategies. The authors propose a multi-decoder model sharing the same encoder among languages and routing languages in different families to different decoders. These approaches share the same interest in expressing the proximity between tasks in the selection of task-specific parameters as our approach. However, our method learn the selection from a latent commonality in data instead of using a predefined selection such as "One language family per decoder" in \citep{kong21multilingual}.

\textbf{Language-specific sub-networks}. \done\todo{}\citet{Frankle19Lottery,liu18rethinking} study techniques to identify the most important parameters for the current task, so that masking the less important parameters during training does not hurt performance. \citet{lin21learning} adapts this idea for multilingual NMT, trying to identify language dependent subsets of parameters by pruning a fine-tuned model. Our approach also aims to map sub-networks to tasks: we do so by masking the output of each layer, rather than masking parameters. Furthermore, \citet{lin21learning} computes the masks via a heuristic selection; while our approach learns the masks with variational techniques.
